### 2024-06-26 manuscript.Rmd

In the following, we give recommendations on how to use the package in typical cases of statistical data analysis and reporting.
It is possible to simply replace all classic `R` code chunks with `reproducibleR` code chunks.
Then, all variables created in the process of a given data analysis will be tested for reproducibility.
However, we advise against this procedure as it is likely that some variables will not exactly reproduce even though all results that researchers find meaningfull will perfectly reproduce.

>>>>

In the following, we give recommendations on how to use the package in typical cases of statistical data analysis and reporting.
It is possible to simply replace all classic `R` code chunks with `reproducibleR` code chunks.
Then, all variables created in the process of a given data analysis will be tested for reproducibility.
However, we advise against this procedure as it is likely that some variables will not exactly reproduce even though all results that researchers find meaningful will perfectly reproduce.
